Fire Damage in Toronto: A Study of Contributing Factors

### 2024-09-27 paper/paper.qmd
Small change to citation

In this paper, we make use R (@citeR) and the tidyverse package (@tidyverse). The data set is from Open Data Toronto (@opendatatoronto). The figures in our study are generated by ggplot (@ggplot2) . We also have used (@sigmoid) when simulating and testing with our data.

>>>>

In this paper, we make use R (@citeR) and the tidyverse package (@tidyverse) with supporting packages sigmoid(@sigmoid) and dplyr(@dplyr). The data set is from Open Data Toronto (@opendatatoronto). The figures in our study are generated by ggplot (@ggplot2).
